### 2017-10-13 Gruba/02-overview.tex

We consider people's \retg{} behavior in social media.
%For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
For simplicity, assuming the microblogs that a user can \ret{} come from those owned by his/her followees.

@@

\begin{table}[tb!]
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
%\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
$G_u$				& gender of user $u$				\\	\midrule
$P_u$				& province of user $u$				\\	\midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
                    & a ratio defined as the number of followers  \\
\raisebox{1.5ex}{$R_{ee}$}  & over that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
$U_t$					& user type (as illustrated in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-2ex}
\end{table}

>>>>

We consider the \retg{} behavior of users in social media.
%For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
For simplicity, assuming the microblogs that a user can \ret{} come from those owned by his/her followees.

@@

\begin{table}[tb!]
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
%\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
$G_u$				& gender of user $u$				\\	\midrule
$P_u$				& province of user $u$				\\	\midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
                    & a ratio defined as the number of followers  \\
\raisebox{1.5ex}{$R_{ee,u}$}  & over that of followees, i.e., $\frac{\#R_u}{\#E_u}$ \\  \midrule
$U_{t,u}$					& user type (as illustrated in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-2ex}
\end{table}

### 2017-10-13 Gruba/03-fe.tex

% jing @ 0927
% back to algorithm for interest features
% add motivation, intuition, etc

%clear points
%road map
%detail of each step, with motivation

@@

With the underlying Sina Microblog Data, Feature Extraction is responsible for ``mining'' the user characteristics, resulting three features for each user.
These features are \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, which constitute the \textit{Feature Data} in \sys{}, i.e., \textit{Feature Data} = \{\textit{Basic Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.

@@

\textit{Basic Feature} employs a vector $I$ to cover the basic info of user.
\begin{equation}
\label{eq:info}
	I = (G_u,\ P_u,\ \#R_u,\ \#E_u,\ R_{ee},\ \ U_t)
\end{equation}
where each variable is illustrated in Table \ref{tbl:fe-info}.
%Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} microblogs and microblogs that are originally created by the user.

@@

Unlike \textit{Basic Feature}, \textit{Behavior Feature} shows several statistics regarding the user's \retg{} behavior.
Such statistics include:
\begin{itemize}
	\item a value for the number of owned microblogs $\#B_u$
	\item a ratio $R_{oc}$ that is defined as the number of \retd{} microblogs over that of originally \twd{}, i.e., $\frac{\#(B_u | flag ==1)}{\#(B_u | flag ==0)}$
	\item values showing the average number of \retd{} and \twd{} microblogs per week: $\#W_r$, $\#W_t$
	\item normalized vectors regarding the time distribution of a user's \retg{}/\twg{} behavior: $P_{rt}\ = (p'_{r0},\ p'_{r1},\ ...,\ p'_{r11})$, $P_{tt}\ = (p'_{t0},\ p'_{t1},\ ...,\ p'_{t11})$, where $p'_{r0}$/$p'_{t0}$ is the probability that the \retg{}/\twg{} activity happens from 0am to 2am, $p'_{r1}$/$p'_{t1}$ is the probability that the \retg{}/\twg{} activity happens from 2am to 4am, and so on.

	\item normalized vectors with respect to the gap distribution of a user's \retg{}/\twg{} behavior: $P_{rg}\ = (p''_{r0},\ p''_{r1},\ ...,\ p''_{r5})$, $P_{tg}\ = (p''_{t0},\ p''_{t1},\ ...,\ p''_{t5})$, in which $p''_{r0}$/$p''_{t0}$ is the probability that the gap between two \retd{}/\twg{} microblogs is within 1 min. Ditto for $p''_{r1}$/$p''_{t1}$ (1 min to 1 hour), $p''_{r2}$/$p''_{t2}$ (1 to 12 hours), $p''_{r3}$/$p''_{t3}$ (12 to 24 hours), $p''_{r4}$/$p''_{t4}$ (24 to 48 hours) and  $p''_{r5}$/$p''_{t5}$ (more than 48 hours).
\end{itemize}

Hence, \textit{Behavior Feature} $H$ per user comes with:
\begin{equation}
\label{eq:beha}
	H = (\#B_u, R_{oc},\ \#W_r,\ P_{rt},\\
    P_{rg},\ \#W_t,\ P_{tt},\ P_{tg})
\end{equation}
% where $\#B_u$, $R_{oc}$, $\#W_r$, $P_t$ and $P_g$ are illustrated as above.

@@

As a result, the \textit{Feature Data} for every user $u$, written as $F(u)$, is given by:
\begin{equation}
\label{eq:fu}
	F(u) = (I,\ H,\ P_f)
\end{equation}
where $I$, $H$ and $P_f$ refer to \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature} separately (see formulas \ref{eq:info}, \ref{eq:beha} and \ref{def:inte}).
And it could be written as a vector:
\begin{equation}
\label{eq:fu-flat}
	F(u) = (G_u, P_u, \#R_s, \#E_s, R_{ee}, U_t, \#B_u, R_{oc},\\
    \#W_r, P_{rt}, P_{rg}, \#W_t, P_{tt}, P_{tg}, P_f)
%(\#R_s, \#E_s, R_{ee}, \#B_s, R_{oc}, U_t, \#W_r, P_t, P_g, P_f)
\end{equation}
where each dimension refers to a data item of \sys{}.

>>>>

@@

With the underlying Sina Microblog Data, the Feature Extraction module is responsible for ``mining'' the user characteristics, and produces three classes of features for each user: \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, referred to as  \textit{Feature Data} in \sys{}.
%, i.e., \textit{Feature Data} = \{\textit{Basic Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.

@@

The \textit{Basic Feature} employs a vector $I$ to depict the basic characteristics of a user $u$.
\begin{equation}
\label{eq:info}
	I_u = (G_u, P_u, \#R_u, \#E_u, R_{ee,u}, U_{t,u}),
\end{equation}
in which the variable details are illustrated in Table \ref{tbl:fe-info}.
%Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} microblogs and microblogs that are originally created by the user.

@@

Unlike \textit{Basic Feature}, the \textit{Behavior Feature} of a user $u$ is certain statistics regarding the \retg{} behavior of $u$, shown below:

\sstab(a) the number of owned microblogs $\#B_u$,

\sstab(b) the ratio $R_{oc,u}$ that is the number of \retd{} microblogs over that of originally \twd{}, i.e., $\frac{\#(B_u | flag ==1)}{\#(B_u | flag ==0)}$,

\sstab(c) the average number of \retd{} and \twd{} microblogs per week: $\#W_{r,u}$ and $\#W_{t,u}$,

\sstab(d) the normalized vectors regarding the time distribution of a user's \retg{}/\twg{} behavior: $P_{rt,u}\ = (p'_{r0},\ p'_{r1},\ ...,\ p'_{r11})$, $P_{tt,u}\ = (p'_{t0},\ p'_{t1},\ ...,\ p'_{t11})$, where $p'_{r0}$/$p'_{t0}$ is the probability that the \retg{}/\twg{} activity happens from 0am to 2am, $p'_{r1}$/$p'_{t1}$ is the probability that the \retg{}/\twg{} activity happens from 2am to 4am, and so on, and

\sstab(e) the normalized vectors with respect to the gap distribution of a user's \retg{}/\twg{} behavior: $P_{rg,u}\ = (p''_{r0},\ p''_{r1},\ ...,\ p''_{r5})$, $P_{tg,u}\ = (p''_{t0},\ p''_{t1},\ ...,\ p''_{t5})$, in which $p''_{r0}$/$p''_{t0}$ is the probability that the gap between two \retd{}/\twg{} microblogs is within 1 min. Ditto for $p''_{r1}$/$p''_{t1}$ (1 min to 1 hour), $p''_{r2}$/$p''_{t2}$ (1 to 12 hours), $p''_{r3}$/$p''_{t3}$ (12 to 24 hours), $p''_{r4}$/$p''_{t4}$ (24 to 48 hours) and  $p''_{r5}$/$p''_{t5}$ (more than 48 hours).

In summary, the \textit{Behavior Feature} $H_u$ of user $u$ consists of the following:

\begin{equation}
\label{eq:beha}
(\#B_u, R_{oc,u}, \#W_{r,u}, P_{rt,u}, P_{rg,u}, \#W_{t,u}, P_{tt,u}, P_{tg,u}).
\end{equation}

% where $\#B_u$, $R_{oc}$, $\#W_r$, $P_t$ and $P_g$ are illustrated as above.

@@

As a result, the \textit{Feature Data} for every user $u$, written as $F(u)$, is given by:
\begin{equation}
\label{eq:fu}
	F(u) = (I,\ H,\ P_f)
\end{equation}
where $I$, $H$ and $P_f$ refer to \textit{Basic Feature}, \textit{Behavior Feature} and \textit{Interest Feature} separately (see formulas \ref{eq:info}, \ref{eq:beha} and \ref{def:inte}).
And it could be written as a vector:
\begin{equation}
\label{eq:fu-flat}
\begin{aligned}
	F(u) = (G_u, P_u, \#R_s, \#E_s, R_{ee}, U_t, \#B_u, R_{oc},\\
    \#W_r, P_{rt}, P_{rg}, \#W_t, P_{tt}, P_{tg}, P_f)
%(\#R_s, \#E_s, R_{ee}, \#B_s, R_{oc}, U_t, \#W_r, P_t, P_g, P_f)
\end{aligned}
\end{equation}
where each dimension refers to a data item of \sys{}.
